Road Segment Prioritization for Bicycle Infrastructure

### 2020-10-30 README.Rmd
commented out reproducibility instructions in readme

Road Segment Prioritization for Bicycle Infrastructure
================

## Missing Data

There are a couple of files that cannot be synced to github due to their
size. These files are neseccary for the scripts to run. Below are links
to where you can download them, and instructions on where to place them
in the repo file structure

Flow Data (2011 Census Origin-Destination Data):

  - Source: <https://www.nomisweb.co.uk/census/2011/bulk/rOD1> —\>
    Choose File **“WU03EW”**
  - Location in Repo: data-raw/flow\_data.csv

Middle Layer Super Output Areas (December 2011) Boundaries:

  - Source:
    <http://geoportal.statistics.gov.uk/datasets/826dc85fb600440889480f4d9dbb1a24_0>
  - Location in Repo: data-raw/MSOA\_2011\_Boundaries/\[Add files here\]

-----

## Scripts

The scripts should be run in the order they are numbered in (and listed
in here). The only exception is \_x\_dodgr\_weighting\_profiles.R.

Check the readme
[here](https://github.com/Hussein-Mahfouz/Bicycle-Network-Optimization)
for detailed info on each script

@@

@@

and these will be the conclusions

>>>>

- Community Detection
- Other Cities

<!-- ## Missing Data -->

<!-- There are a couple of files that cannot be synced to github due to their -->
<!-- size. These files are neseccary for the scripts to run. Below are links -->
<!-- to where you can download them, and instructions on where to place them -->
<!-- in the repo file structure -->

<!-- Flow Data (2011 Census Origin-Destination Data): -->

<!--   - Source: <https://www.nomisweb.co.uk/census/2011/bulk/rOD1> —\> -->
<!--     Choose File **“WU03EW”** -->
<!--   - Location in Repo: data-raw/flow\_data.csv -->

<!-- Middle Layer Super Output Areas (December 2011) Boundaries: -->

<!--   - Source: -->
<!--     <http://geoportal.statistics.gov.uk/datasets/826dc85fb600440889480f4d9dbb1a24_0> -->
<!--   - Location in Repo: data-raw/MSOA\_2011\_Boundaries/\[Add files here\] -->

<!-- ----- -->

<!-- ## Scripts -->

<!-- The scripts should be run in the order they are numbered in (and listed -->
<!-- in here). The only exception is \_x\_dodgr\_weighting\_profiles.R. -->

<!-- Check the readme -->
<!-- [here](https://github.com/Hussein-Mahfouz/Bicycle-Network-Optimization) -->
<!-- for detailed info on each script -->

@@

### Hello

@@
